Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-18 paper/main.tex
restructure contrasts section

\item revise captions of Table 1 + 3; regressors that are based on the other
    stimulus for control purposes are now dropped from the table; but mention in
        Statistical Analysis / Statistical Model)

\item what do we need to check to ensure subsequent analyses are valid;
    a) correlation of regressors (first "sanity check" but more a prerequisite)
    b) negative controls (actual sanity check)

@@

\begin{itemize}
\item mehrere Kontraste in VIS genommen, hier einer berichtet: Teil aus
    Discussion in Results hochnehmen
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item \citep{bartels2004mapping, hasson2004intersubject}
    \item VIS: "best contrast was chosen"
\end{itemize}

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{actually, it was a box car of 200 ms after
starting with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\paragraph{PPA Contrasts} \todo{maybe repeat key questions (cf. intro) here}

% intro
To test the robustness of our approach, we then operationalized the
perception of spatial information compared to the perception of ``non-spatial''
information differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).\todo{make ref to what is no "Audio-description: annotation"}
% thus: primary contrasts
For each stimulus, we chose one contrast to be ``primary contrast'' for further
inspection and a detailed report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or
faces.

% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

\todo[inline]{one could write more about the different contrast in Segupta et
al. here, but imo it's sufficient to point that out in the results given that
all subjects except two used the strict set given contrasts of VIS study and
that the ``best working'' will be used}

\todo[inline]{Nevertheless, state it in one sentence and check Berman, M. G. et al. Evaluating functional localizers: The case of the FFA. NeuroImage 50, 56–71 (2010)}

Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

@@

% intro
Finally, we created several contrasts as negative control for both stimuli.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts possibly correlated with a accompanying change
in the soundscape.
% AV stimulus
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
condition (texttt{vno\_cut} for negative control purposes (see Table
\ref{tab:av-contrasts}) by using regressors based on regressors of the AD
stimulus. One contrast (\texttt{vs\_new} > \texttt{vpe\_old})  was created by
contrasting nouns spoken by the narrator.

@@

\subsubsection{model testing / GLM computations}

>>>>

    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung

    \item revise captions of Table 1 + 3 (regressors based on annotation of
    the other FG stimulus are now dropped from the table but mentioned in
    section "statistial model / contrasts")

@@

\begin{itemize}
\item adjust structure of results to structure of discussion
\item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
\end{itemize}

\noindent Discussion
\begin{itemize}
\item umschreiben gemäß neuer Schwerpunktsetzung in Intro \& Method-Section
    \item \citep{bartels2004mapping, hasson2004intersubject}
    \item mehr zum Thema VIS( "best contrast was chosen")
\end{itemize}

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{actually, it was a box car of 200 ms starting
with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\paragraph{PPA Contrasts}

In this study, we investigated if increased hemodynamic activty in the PPA that
is usually defined by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that we annotated in a audio-visual movie
and its audio-description.
% intro
To test the robustness of our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010);
but they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

@@

% intro
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. results and discussion}
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory cue of switching to another
setting.

@@

\paragraph{GLM computations \& stuff}
